% T I T L E   P A G E
% -------------------
% Last updated June 14, 2017, by Stephen Carr, IST-Client Services
% The title page is counted as page `i' but we need to suppress the
% page number. Also, we don't want any headers or footers.
\pagestyle{empty}
\pagenumbering{roman}

% The contents of the title page are specified in the "titlepage"
% environment.
\begin{titlepage}
        \begin{center}
        \vspace*{1.0cm}

        \Huge
        {\bf Deformation-Driven Element Packings }

        \vspace*{1.0cm}

        \normalsize
        by \\

        \vspace*{1.0cm}

        \Large
        Reza Adhitya Saputra \\

        \vspace*{3.0cm}

        \normalsize
        A thesis \\
        presented to the University of Waterloo \\ 
        in fulfillment of the \\
        thesis requirement for the degree of \\
        Doctor of Philosophy \\
        in \\
        Computer Science \\

        \vspace*{2.0cm}

        Waterloo, Ontario, Canada, 2020 \\

        \vspace*{1.0cm}

        \copyright\ Reza Adhitya Saputra 2020 \\
        \end{center}
\end{titlepage}

% The rest of the front pages should contain no headers and be numbered using Roman numerals starting with `ii'
\pagestyle{plain}
\setcounter{page}{2}

\cleardoublepage % Ends the current page and causes all figures and tables that have so far appeared in the input to be printed.
% In a two-sided printing style, it also makes the next page a right-hand (odd-numbered) page, producing a blank page if necessary.

 
% E X A M I N I N G   C O M M I T T E E (Required for Ph.D. theses only)
% Remove or comment out the lines below to remove this page
\begin{center}\textbf{Examining Committee Membership}\end{center}
  \noindent
The following served on the Examining Committee for this thesis. The decision of the Examining Committee is by majority vote.
  \bigskip
  
  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
External Examiner: \>  YYY YYY \\ 
\> Professor, Dept. of YYY, University of YYY \\
\end{tabbing} 
  \bigskip
  
  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Supervisor(s): \> Craig S. Kaplan \\
\> Professor, Dept. of Computer Science, University of Waterloo \\
\end{tabbing}
  \bigskip
  
  \noindent
  \begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Internal Member: \> Christopher Batty \\
\> Professor, Dept. of Computer Science, University of Waterloo \\
\end{tabbing}
  \bigskip
  
  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Internal-External Member: \> YYY YYY \\
\> Professor, Dept. of YYY, University of Waterloo \\
\end{tabbing}
  \bigskip
  
  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Other Member(s): \> Daniel Vogel \\
\> Professor, Dept. of Computer Science, University of Waterloo \\
\end{tabbing}

\cleardoublepage

% D E C L A R A T I O N   P A G E
% -------------------------------
  % The following is a sample Delaration Page as provided by the GSO
  % December 13th, 2006.  It is designed for an electronic thesis.
%\phantomsection
%\addcontentsline{toc}{chapter}{Author's Declaration}
\begin{center}\textbf{Author's Declaration}\end{center}
  \noindent

\newtext{
This thesis consists of materials which I authored or co-authored: 
see Statement of Contributions. }
This is a true copy of the thesis, 
including any required final revisions,
as accepted by my examiners

  \bigskip
  
  \noindent
I understand that my thesis may be made electronically available to the public.

\cleardoublepage


%\phantomsection
%\addcontentsline{toc}{chapter}{Statement of Contribution}
\begin{center}\textbf{Statement of Contribution}\end{center}
  \noindent

\newtext{
This thesis was built from previous publications authored by myself,
{Dr. Craig S. Kaplan}, and Dr. Paul Asente.
}

\newtext{
FLOWPAK in Chapter~\ref{chapter_flowpak} was initially conducted with 
Dr. Paul Asente, and Dr. Radom\'{\i}r M\v{e}ch at Adobe Research in San Jose, CA.
FLOWPAK is also discussed in greater detail in our publication ``FLOWPAK: Flow-based Ornamental Element Packing''~\cite{Saputra2017} and in our patent ``Computerized Generation of Ornamental Designs by Placing Instances of Simple Shapes in Accordance With a Direction Guide''~\cite{Asente2020}.
}

\newtext{
RepulsionPak in Chapter~\ref{chapter_repulsionpak} and Quantitative Metrics in Chapter~\ref{chapter_qualitative_metrics} 
were taken from ``RepulsionPak: Deformation-Driven Element Packing with Repulsion Forces''~\cite{Saputra2018} and 
``Improved Deformation-Driven Element Packing with RepulsionPak''~\cite{Saputra2019}.
}

\newtext{
AnimationPak in Chapter~\ref{chapter_animationpak} was taken from ``AnimationPak: Packing Elements with Scripted Animations''~\cite{Saputra2020}.
}


\cleardoublepage


% A B S T R A C T
% ---------------
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}
\begin{center}\textbf{Abstract}\end{center}

\newtext{
We present three methods to fill a container shape with deformable instances of geometric elements selected from a library,
creating a 2D artistic composition called a packing.}
\newtext{
The first method is FLOWPAK that deforms elements to flow along a vector field interpolated
from user-supplied strokes, giving a sense of visual flow to the final composition.
%FLOWPAK constructs streamlines that conform to the vector field, and places an
%element over each streamline. 
}
\newtext{
The second method is RepulsionPak that utilizes physical simulations to deform
elements, each is represented as a mass-spring system, allowing them to deform
to achieve a better fit with their neighbours and the container.
%RepulsionPak start with an initial random placement of small elements and gradually transform them using 
%repulsion forces that trade off between the evenness of the packing and the deformations of the individual elements.
}
\newtext{
The last method is AnimationPak that creates animated packings
by arranging animated two-dimensional elements inside a static
container. We represent animated elements in a three-dimensional
spacetime domain, and view the animated packing problem as a
three-dimensional packing in that domain. 
%Every element is represented as a discretized spacetime mesh. 
%In a physical simulation, meshes grow and repel each other, consuming the negative space
%in the container. The final animation frames are cross sections of
%the three-dimensional packing at a sequence of time values. 
}
\newtext{
Finally, we propose statistical methods for measuring the evenness of
negative space in a 2D packing, which provide a quantitative
means of evaluating and comparing packing algorithms.
}

\cleardoublepage

% A C K N O W L E D G E M E N T S
% -------------------------------

\begin{center}\textbf{Acknowledgements}\end{center}

I would like to thank all people who have helped me during my PhD study:


\begin{itemize}  
\item Craig S. Kaplan, for being the best teacher.
\item Paul Asente, for his guidance and wisdom. 
\item Radom\'ir M\v{e}ch, for the internship and the help with FLOWPAK paper. 
\item Daichi Ito, for the discussion about FLOWPAK and creating a packing with RepulsionPak.
\item Yusuf Umar, for designing ornamental elements and the box bird in Figure~\ref{bird_square}.
\item Dietrich Stoyan, for the discussion about spatial statistics.
\item Danny Kaufman, for the discussion about physical simulations.
\item Steve Mann, for giving me valuable lessons.
\item Bill Cowan, for his advice.
\item Christopher Batty and Dan Vogel, for being my PhD committee members.
\item Matt Thorne, Alex Pytel, and Tyler Nowicki, for all the lunches together. 
\item All my running friends in Kitchener-Waterloo and ultra running community in \mbox{Ontario}, 
who teach me on how to keep grinding.
\end{itemize}

\cleardoublepage

% D E D I C A T I O N
% -------------------

\begin{center}\textbf{Dedication}\end{center}

For my Mom, Dad, and my sister.
\cleardoublepage

% T A B L E   O F   C O N T E N T S
% ---------------------------------
\renewcommand\contentsname{Table of Contents}
\tableofcontents
\cleardoublepage
\phantomsection    % allows hyperref to link to the correct page

% L I S T   O F   T A B L E S
% ---------------------------
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% L I S T   O F   F I G U R E S
% -----------------------------
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% GLOSSARIES (Lists of definitions, abbreviations, symbols, etc. provided by the glossaries-extra package)
% -----------------------------
\printglossaries
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% Change page numbering back to Arabic numerals
\pagenumbering{arabic}

