% T I T L E   P A G E
% -------------------
% Last updated June 14, 2017, by Stephen Carr, IST-Client Services
% The title page is counted as page `i' but we need to suppress the
% page number. Also, we don't want any headers or footers.
\pagestyle{empty}
\pagenumbering{roman}

% The contents of the title page are specified in the "titlepage"
% environment.
\begin{titlepage}
        \begin{center}
        \vspace*{1.0cm}

        \Huge
        {\bf Deformation-Driven Element Packings }

        \vspace*{1.0cm}

        \normalsize
        by \\

        \vspace*{1.0cm}

        \Large
        Reza Adhitya Saputra \\

        \vspace*{3.0cm}

        \normalsize
        A thesis \\
        presented to the University of Waterloo \\ 
        in fulfillment of the \\
        thesis requirement for the degree of \\
        Doctor of Philosophy \\
        in \\
        Computer Science \\

        \vspace*{2.0cm}

        Waterloo, Ontario, Canada, 2020 \\

        \vspace*{1.0cm}

        \copyright\ Reza Adhitya Saputra 2020 \\
        \end{center}
\end{titlepage}

% The rest of the front pages should contain no headers and be numbered using Roman numerals starting with `ii'
\pagestyle{plain}
\setcounter{page}{2}

\cleardoublepage % Ends the current page and causes all figures and tables that have so far appeared in the input to be printed.
% In a two-sided printing style, it also makes the next page a right-hand (odd-numbered) page, producing a blank page if necessary.

 
% E X A M I N I N G   C O M M I T T E E (Required for Ph.D. theses only)
% Remove or comment out the lines below to remove this page
\begin{center}\textbf{Examining Committee Membership}\end{center}
  \noindent
The following served on the Examining Committee for this thesis. The decision of the Examining Committee is by majority vote.
  \bigskip
  
  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
External Examiner: \>  Bruce Bruce \\ 
\> Professor, Dept. of Philosophy of Zoology, University of Wallamaloo \\
\end{tabbing} 
  \bigskip
  
  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Supervisor(s): \> Craig S. Kaplan \\
\> Professor, Dept. of Computer Science, University of Waterloo \\
\end{tabbing}
  \bigskip
  
  \noindent
  \begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Internal Member: \> Pamela Python \\
\> Professor, Dept. of Zoology, University of Waterloo \\
\end{tabbing}
  \bigskip
  
  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Internal-External Member: \> Deepa Thotta \\
\> Professor, Dept. of Philosophy, University of Waterloo \\
\end{tabbing}
  \bigskip
  
  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Other Member(s): \> Leeping Fang \\
\> Professor, Dept. of Fine Art, University of Waterloo \\
\end{tabbing}

\cleardoublepage

% D E C L A R A T I O N   P A G E
% -------------------------------
  % The following is a sample Delaration Page as provided by the GSO
  % December 13th, 2006.  It is designed for an electronic thesis.
%\phantomsection
%\addcontentsline{toc}{chapter}{Author's Declaration}
\begin{center}\textbf{Author's Declaration}\end{center}
  \noindent

\mynote{choppy pdflatex rendering why lol}

\newtext{
This thesis consists of materials which I authored or co-authored: 
see Statement of Contributions. }
This is a true copy of the thesis, 
including any required final revisions,
as accepted by my examiners

  \bigskip
  
  \noindent
I understand that my thesis may be made electronically available to the public.

\cleardoublepage


%\phantomsection
%\addcontentsline{toc}{chapter}{Statement of Contribution}
\begin{center}\textbf{Statement of Contribution}\end{center}
  \noindent

\newtext{
This thesis was built from previous publications authored by myself,
{Dr. Craig S. Kaplan}, Dr. Paul Asente, and Dr. Radom\'{\i}r M\v{e}ch.
}

\newtext{
FLOWPAK in Chapter~\ref{chapter_flowpak} was initially conducted with 
Dr. Paul Asente, and Dr. Radom\'{\i}r M\v{e}ch at Adobe Research in San Jose, CA.
FLOWPAK is also discussed in greater detail in our publication ``FLOWPAK: Flow-based Ornamental Element Packing''~\cite{Saputra2017} and in our patent ``Computerized Generation of Ornamental Designs by Placing Instances of Simple Shapes in Accordance With a Direction Guide''~\cite{Asente2020}.
RepulsionPak in Chapter~\ref{chapter_repulsionpak} and Quantitative Metrics in Chapter~\ref{chapter_qualitative_metrics} 
were taken from ``RepulsionPak: Deformation-Driven Element Packing with Repulsion Forces''~\cite{Saputra2018} and 
``Improved Deformation-Driven Element Packing with RepulsionPak''~\cite{Saputra2019}.
AnimationPak in Chapter~\ref{chapter_animationpak} was taken from ``AnimationPak: Packing Elements with Scripted Animations''~\cite{Saputra2020}.
}


\cleardoublepage


% A B S T R A C T
% ---------------
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}
\begin{center}\textbf{Abstract}\end{center}

\mynote{
\begin{itemize}
\item one page stating what the thesis is about
\item highlight the contributions of the thesis
\end{itemize}
}

\cleardoublepage

% A C K N O W L E D G E M E N T S
% -------------------------------

\begin{center}\textbf{Acknowledgements}\end{center}

I would like to thank all the little people who made this thesis possible.


\begin{itemize}  
\item Craig S. Kaplan
\item Paul Asente 
\item Radom\'ir M\v{e}ch 
\item Daichi Ito
\item Dietrich Stoyan 
\item Danny Kaufman
\item All my running friends in Kitchener-Waterloo and trail/ultrarunning community in Ontario. 
\end{itemize}

\cleardoublepage

% D E D I C A T I O N
% -------------------

\begin{center}\textbf{Dedication}\end{center}

This is dedicated to my family.
\cleardoublepage

% T A B L E   O F   C O N T E N T S
% ---------------------------------
\renewcommand\contentsname{Table of Contents}
\tableofcontents
\cleardoublepage
\phantomsection    % allows hyperref to link to the correct page

% L I S T   O F   T A B L E S
% ---------------------------
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% L I S T   O F   F I G U R E S
% -----------------------------
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% GLOSSARIES (Lists of definitions, abbreviations, symbols, etc. provided by the glossaries-extra package)
% -----------------------------
\printglossaries
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% Change page numbering back to Arabic numerals
\pagenumbering{arabic}

